\documentclass[11pt]{article}
 
\usepackage{mathtext}         % если нужны русские буквы в формулах (не обязательно)
\usepackage[T2A]{fontenc}     % внутренняя T2A кодировка TeX
\usepackage[russian]{babel}   % включение переносов
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\pagestyle{empty} % нумерация выкл.
\addtolength{\textheight}{1.75in}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{color}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{fontawesome}

\definecolor{gray}{rgb}{0.4,0.4,0.4}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\begin{document}

\begin{center}
\noindent {\sffamily{\Huge{\textbf{ Igor Timofeev }}}}
\end{center}
 
\vspace{0.5em}

\begin{multicols}{2}

GitHub: \href{https://github.com/eluator}{github.com/eluator}

LinkedIn: \href{https://www.linkedin.com/in/itimofeev}{linkedin.com/in/itimofeev}

\columnbreak

tiv.eluator@gmail.com

+381621921949, Serbia

\end{multicols} 
\hrule
 
\begin{multicols}{2}
 
\noindent {\textbf{Enployement History:}}
\begin{itemize}

\item may 2022 - january 2024, Gero: Development of denoising and batch removal techniques in RNA-seq bulk and single-cell data. Obtaining embeddings of cellular perturbations to evaluate the functional similarities among them. \href{https://openaccess.thecvf.com/content/ICCV2021/papers/Xu_Multi-VAE_Learning_Disentangled_View-Common_and_View-Peculiar_Visual_Representations_for_Multi-View_ICCV_2021_paper.pdf}{Multi-VAE}, \href{https://arxiv.org/abs/1603.02514}{SemiVAE}, \href{https://arxiv.org/abs/1802.05983}{FactorVAE}, \href{https://arxiv.org/abs/1907.04809}{iVAE}, \href{https://docs.scvi-tools.org/en/stable/api/reference/scvi.model.SCVI.html#scvi.model.SCVI}{ScVI}, \href{https://arxiv.org/abs/1509.05982}{DVAE}, \href{https://www.degruyter.com/document/doi/10.1515/sagmb-2016-0072/html}{FC1000}, etc. Enrichment analysis, differential expression, leverage score and cell-cycle classification from \href{https://pubmed.ncbi.nlm.nih.gov/35688146/}{Perturb-seq}, noise estimation from \href{https://www.biorxiv.org/content/10.1101/2022.06.23.497402v1}{this paper} and \href{https://arxiv.org/abs/cond-mat/0108023}{A Random Matrix Approach to Cross-Correlations}.

\item march 2021 - august 2021, Yandex: Product analyst for Yandex Search. Improving offline Entity Search metrics, analyzing growth points and customer preferences.

\item august 2020 - february 2021, IE Shapiro Leonid Lvovich: Option pricing model development using machine learning and Python. Fitting asset prices with options data. FFT and Lewis method was used for option prices calculation and asset price was modeled by tempered stable distribution.

\end{itemize}

\vspace{0.5em}

\columnbreak

\noindent {\textbf{Education:}}

\vspace{0.5em}

St. Petersburg State University, 

Department of Mathematics and Mechanics,

Specialist degree in Astronomy (equivalent of Bachelor + Master),

Sep, 2014 - June, 2019.

\vspace{0.5em}

\indent {\textbf{Degree Thesis:}} 

\vspace{0.5em}

\indent \indent Topic: "The Effect of Close Approach to a Planet 

\indent \indent on the Rotation of an Asteroid".

\indent \indent In this work I have developed a program in 
\indent \indent C++ using Boost library and numerical methods 
\indent \indent for calculating an asteroid trajectory in the Solar 
\indent \indent system. \href{https://github.com/eluator/dipvlom}{\faicon{github}}
 
\vspace{0.5em}

\noindent {\textbf{Second Education (interrupted):}}

National Research University Higher School of Economics,

Master of Computational Biology and Bioinformatics,

Sep, 2021 - Apr, 2022

I started a scientific work about aging clocks and finished one semester of Molecular Biology, Machine learning, Algorithms, Clifford Algebras, and Numerical Calculus, I partially took an Algorithms in Bioinformatics course as well. Unfortunately, the education was not finished due to the war in Ukraine.

\vspace{0.5em}

\end{multicols}

\newpage

\begin{multicols}{2}

\noindent {\textbf{Additional education and competitions:}}
\begin{itemize}


\item \href{https://bioinf.me/education/summer/2019}{Bioinformatics Summer School 2019} on the topic “Bioinformatics in Research of Aging and Biological Development” and the project. \href{https://github.com/eluator/MCMC_bioinf_summer_school_2019}{\faicon{github}}

\item 4th place in SignalNeuroHack hackathon with Huawei research project. \href{https://github.com/eluator/SignalNeuroHackTasks}{\faicon{github}}

\item Completed the course \href{https://dlcourse.ai/}{“Deep Learning на пальцах (Put Simply)”} by Computer Science Center and Novosibirsk State University \href{https://github.com/eluator/dlcourse_ai}{\faicon{github}}. Also Reinforcement Learning tasks using DQN algorithm and Policy Gradient \href{https://github.com/eluator/JetBrainsInternship}{\faicon{github}}.

\item Specialization “Machine Learning and Analysis” by Yandex on Coursera \href{https://github.com/eluator/Coursera_ML}{\faicon{github}}.

\item \href{https://stepik.org/users/19741243/certificates}{Stepik courses certificates}.

\item Some lectures and books in addition to university literature: Blastim courses, STAT115 Harvard, Molecular Biophysics(Eric Lindahl), Deep Generative Modeling, Watanabe, David Tong lectures, etc.

\item \href{https://www.alignmentforum.org/posts/vakhhNHduW9gmENTW/announcing-new-round-of-key-phenomena-in-ai-risk-reading}{Reading Group Key Phenomena in AI Risk}, reading group in Belgrade about \href{https://course.aisafetyfundamentals.com/alignment?_gl=1*1xg9r59*_ga*MTgyMzIzOTUwNS4xNjk4MzQwMDQy*_ga_LGQ75B1P00*MTcwNjcxMTA1OC4zLjEuMTcwNjcxMTA5MC4wLjAuMA..}{AI Safety Fundamentals}, \href{https://www.linkedin.com/posts/effective-altruism-serbia_easerbia-makedifference-effectivealtruism-activity-7046076217321566208-SMq2/}{EA Serbia Introductory Course}.


\vspace{0.5em}

\columnbreak

\noindent {\textbf{Knowledge and skills:}}

\begin{itemize}

\item Machine Learning: PyTorch, TensorFlow, scikit-learn, etc.

\item Python, C/C++.

\item Calculus, Algebra, Numerical analysis, Probability theory and Mathematical Statistics, Algorithms and Data Structures.

\item Physics: Statistical Physics, Quantum Mechanics, etc.

\item Basics of Molecular Biology, partially Bioinformatics: BLAST, differential expression,enrichment, batch effect removal, RNA-seq, partially Biophysics.

\item Data Analysis: SQL, Statistical Hypothesis Testing \href{https://github.com/eluator/DataAnalysisInR}{\faicon{github}}.

\end{itemize}


\end{itemize}
\end{multicols}


\end{document}             % End of document.

\begin{itemize}